Light inextensible strings under tension in the Schwarzschild geometry

### 2018-09-06 string.tex
include self-intersecting strings

Figure~\ref{closest_approach} shows strings indexed by distance of
approach to the singularity, which occurs at~$\phi=0$.  Strings with a
sufficiently close passage to the event horizon self-intersect;
numerical methods show that the critical value is~$\simeq
1.076109317$, with an uncertainty of 1 in the last digit: if a string
with two free ends passes closer than this, it forms a closed loop.

\begin{figure}[h!]
\centering
\includegraphics{closest_approach.pdf}
\caption{Strings arranged by closest approach to the event horizon}
\label{closest_approach}
\end{figure}

>>>>

Figure~\ref{closest_approach_non_self_intersecting} shows
nonselfintersecting strings indexed by distance of approach to the
singularity, which occurs at~$\phi=0$.  Strings with a sufficiently
close passage to the event horizon self-intersect; numerical methods
show that the critical value is~$\simeq 1.076109317$, with an
uncertainty of 1 in the last digit: if a string with two free ends
passes closer than this, it forms a closed loop.

\begin{figure}[h!]
\centering
\includegraphics{closest_approach_nonselfintersecting.pdf}
\caption{Strings arranged by closest approach to the event horizon:
  non-self-intersecting strings}
\label{closest_approach_non_self_intersecting}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics{closest_approach_selfintersecting.pdf}
\caption{Strings arranged by closest approach to the event horizon:
 self-intersecting strings}
\label{closest_approach_self_intersecting}
\end{figure}
